COG-ED Manuscript

### 2022-06-09 06_Paper/COG-ED/Manuscript.Rmd
implemented Editor's comment
added 1vs1 description

### CAD Paradigm
Figure\ 1 illustrates how different modifications of the COG-ED paradigm [@Westbrook2013] return SVs that do or do not reflect the true preference of a hypothetical participant, who likes 2-back most, 3-back less, and 1-back least (for reasons of clarity there are only three levels in the example).
The COG-ED paradigm, which compares every more difficult level with 1-back sets the SV of 1-back to 1, regardless of the response pattern.
Adding a comparison of the more difficult levels with each other allows the SVs of those two levels to be more differentiated, but leaves the SV of 1-back unchanged.
Adding those same pairs again, but with the oppositve assignment of fixed and flexible level, does approach the true preference, but has two disadvantages.
First, the SVs are still quite alike across levels due to the fact that every more difficult level has only been compared with the easiest level, and second, having more task levels than just three would lead to an exponential increase in comparisons.
Therefore, the solution lies in reducing the number of necessary comparisons by presenting only one effort discounting round for each possible pair of levels after determining for each pair which level should be fixed and which should be flexible.
In each pair, the level chosen by the participant at least two out of three times will be used as the level with a flexible value, which starts at 1€ and is changed in every iteration.
The other level in the pair will be set to a fixed value of 2€.
Then, the effort discounting sensu Westbrook [-@Westbrook2013] begins, but with all possible pairs and with the individually determined assignment of fixed and flexible level.
The order in which the pairs are presented will be fully randomized, and each pair will go through all iteration steps of adding/subtracting 0.50\ €, 0.25\ €, 0.13\ €, 0.06\ €, 0.03\ €, 0.02\ € to/from the flexible level's reward (each adjustment half of the previous one, rounded to two decimals) before moving on to the next one.
This procedure allows to compute SVs based on actual individual preference instead of objective task load.
For each pair, the SV of the flexible level is 1, as it was preferred when faced with equal rewards, and the SV of the fixed level is the final reward of the flexible level divided by 2\ €.
Each level's "global" SV is calculated as the mean of this level's SVs from all pairs in which it appeared.
If the participant has a clear preference for one level, this level's SV will be 1.
If not, then no level's SV will be 1, but each level's SV can still be interpreted as an absolute and relative value, so each participant's effort discounting behaviour can still be quantified.
The interpretation of SVs in Westbrook [-@Westbrook2013] was "The minimum relative reward required for me to choose 1-back over this level".
So if the SV of 3-back was 0.6, the participant would need to be rewarded with at least 60\ % of what they are being offered for doing 3-back to do 1-back instead, forgoing the higher reward for 3-back.
In this study, the SV can be interpreted as "The minimum relative reward required for me to choose any other level over this level".
Therefore, an SV of 1 indicates that this level is preferred over all others, while SVs lower than 1 indicate that in at least one pair, a different level was preferred over this one.

@@

The results of each analysis will be assessed on the basis of both $p$-value and the Bayes factor $BF10$, calculated with the *BayesFactor* package[@Morey2021] using the default prior widths of the functions *anovaBF*, *lmBF* and *regressionBF*.

>>>>

### CAD Paradigm
Figure\ 1 illustrates how different modifications of the COG-ED paradigm [@Westbrook2013] return SVs that do or do not reflect the true preference of a hypothetical participant, who likes 2-back most, 3-back less, and 1-back least (for reasons of clarity there are only three levels in the example).
The COG-ED paradigm, which compares every more difficult level with 1-back sets the SV of 1-back to 1, regardless of the response pattern.
Adding a comparison of the more difficult levels with each other allows the SVs of those two levels to be more differentiated, but leaves the SV of 1-back unchanged.
Adding those same pairs again, but with the oppositve assignment of fixed and flexible level, does approach the true preference, but has two disadvantages.
First, the SVs are still quite alike across levels due to the fact that every more difficult level has only been compared with the easiest level, and second, having more task levels than just three would lead to an exponential increase in comparisons.
Therefore, the solution lies in reducing the number of necessary comparisons by presenting only one effort discounting round for each possible pair of levels after determining for each pair which level should be fixed and which should be flexible.
This will be determined by presenting each possible pair of levels on screen with the question "Would you prefer 1\ € for level A or 1\ € for level B?".
Participants respond by clicking the respective on-screen button.
Each pair will be presented three times, resulting in 18 presented pairs, which are fully randomized in order and in the assignment of which level is on the left or right of the screen.
For each pair, the level that was chosen by the participant at least two out of three times will be used as the level with a flexible value, which starts at 1\ € and is changed in every iteration.
The other level in the pair will be set to a fixed value of 2\ €.
Then, the effort discounting sensu Westbrook [-@Westbrook2013] begins, but with all possible pairs and with the individually determined assignment of fixed and flexible level.
The order in which the pairs are presented will be fully randomized, and each pair will go through all iteration steps of adding/subtracting 0.50\ €, 0.25\ €, 0.13\ €, 0.06\ €, 0.03\ €, 0.02\ € to/from the flexible level's reward (each adjustment half of the previous one, rounded to two decimals) before moving on to the next one.
This procedure allows to compute SVs based on actual individual preference instead of objective task load.
For each pair, the SV of the flexible level is 1, as it was preferred when faced with equal rewards, and the SV of the fixed level is the final reward of the flexible level divided by 2\ €.
Each level's "global" SV is calculated as the mean of this level's SVs from all pairs in which it appeared.
If the participant has a clear preference for one level, this level's SV will be 1.
If not, then no level's SV will be 1, but each level's SV can still be interpreted as an absolute and relative value, so each participant's effort discounting behaviour can still be quantified.
The interpretation of SVs in Westbrook [-@Westbrook2013] was "The minimum relative reward required for me to choose 1-back over this level".
So if the SV of 3-back was 0.6, the participant would need to be rewarded with at least 60\ % of what they are being offered for doing 3-back to do 1-back instead, forgoing the higher reward for 3-back.
In this study, the SV can be interpreted as "The minimum relative reward required for me to choose any other level over this level".
Therefore, an SV of 1 indicates that this level is preferred over all others, while SVs lower than 1 indicate that in at least one pair, a different level was preferred over this one.

@@

The results of each analysis will be assessed on the basis of both $p$-value and the Bayes factor $BF10$, calculated with the *BayesFactor* package[@Morey2021] using the default prior widths of the functions *anovaBF*, *lmBF* and *regressionBF*.
We will consider a $BF10$ close to or above 3/10 as moderate/strong evidence for the alternative hypothesis, and a $BF10$ close to or below .33/.10 as moderate/strong evidence for the null hypothesis [@Wetzels2015].
